Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-03-05 paper/current/main.tex
revise_math_part

%
% Subsection: Mathematical Exploration
%
\subsection*{Mathematical explanation}

@@

In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
Let's denote $\mathpzc{N}_i$ as the neighborhood set of organization i, which are organizations with non-zero co-affiliation to organization i.
Then, the total flux to or from $i$ can be written as

\begin{equation}
    \mu_{i} = \sum_{k\in\mathpzc{N}_i} t_{ik} \propto M_i
\end{equation}

@@

\begin{equation}
    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k\in\mathpzc{N}_i} {\mu_k}\exp(\cos(v_i,v_k))}
\end{equation}

@@

\begin{equation}
    \label{eq:real_embedding_relationship}
    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k\in\mathpzc{N}_i} \exp(\cos(v_k,v_i))}
\end{equation}

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/approxi_proof.png}
    \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary. With facts that the denominator is not calculated entirely in the negative sampling strategies and the cosine similarity of in-vectors is used as a measure of affinity in general, Eq. \ref{eq:skipgram_conditional_expanded} and Eq. \ref{eq:real_embedding_relationship} share a similar functional form (or Eq.~\ref{eq:real_embedding_relationship} is a special case of Eq. ~\ref{eq:skipgram_conditional_expanded}).

>>>>

%
% Subsection: Mathematical Exploration
%
\subsection*{Mathematical connection between gravity model and neural embedding }

@@

In the case of scientific co-affiliation, all movements are without direction (symmetric), meaning that  $T_{ij} = T_{ji}$.
Let's denote $N$ as set of organizations in the data.
Then, the total flux to or from $i$ can be written as

\begin{equation}
    \mu_{i} = \sum_{k \in N} T_{ik} \propto M_i
\end{equation}

@@

\begin{equation}
    p(j|i) \propto \frac{{\mu_j}\exp(\cos(v_i,v_j)}{\sum_{k \in N} {\mu_k}\exp(\cos(v_i,v_k))}
\end{equation}

@@

\begin{equation}
    \label{eq:real_embedding_relationship}
    p(j|i) \propto \frac{\exp(\cos(v_j, v_i))}{\sum_{k \in N} \exp(\cos(v_k,v_i))}
\end{equation}

@@

%
% Figure - Conditional Probability
%
\begin{figure}
    \centering
    \includegraphics[width=0.8\columnwidth]{\figdir/Math/use_all_log.pdf}
    \caption{Relationship between the conditional probability $p(j|i)$ \ref{eq:flux_conditional_prob} which is measured in the data and approximate functional form Eq. \ref{eq:real_embedding_relationship}}.
    \label{fig:real_embedding_relationship}
\end{figure}

@@

where $v_w$ and $v'_w$ are ``input'' and ``output'' vector representations of each word in the vocabulary. With facts that the cosine similarity of in-vectors is used as a measure of affinity in general, Eq. \ref{eq:skipgram_conditional_expanded} and Eq. \ref{eq:real_embedding_relationship} share a similar functional form, or exact same if vectors are normalized.
